Insert the article title here

### 2018-08-09 writeup/manuscript.tex
Fixing comment on Proulx

A striking example of the effect of strategy is given by Boot and colleagues\cite{boot2006}. They asked participants to monitor a cluttered display for an object changing colour or object onset. Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and this was negatively correlated with detection performance. Proulx\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they claim that around a third of participants were unaware of the search strategy they employed.

>>>>

A striking example of the effect of strategy is given by Boot and colleagues\cite{boot2006}. They asked participants to monitor a cluttered display for an object changing colour or object onset. Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and this was negatively correlated with detection performance. Proulx\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained some of the variation in how participants did in an attentional capture task. However, only a third of participants were unaware of the search strategy they employed.
